### 2019-01-21 journal/experiments.tex
experiments
bring in coverage localization

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{comment}                                               %
\begin{figure}                                                %
{\scriptsize                                                  %
\begin{code}                                                  %
{\bf Diff of old ($<$) vs new ($>$) for 115 patch (portion):} %
...                                                           %
<             vp[1] = OBJECT\_TO\_JSVAL(thisp);               %
<         \} else \{                                          %
<             ok = OBJ\_GET\_PROPERTY(cx, thisp, id, \&v);    %
<         \}                                                  %
...                                                           %
<                   a->avail = (jsuword)sp;                   %
<               \}                                            %
...                                                           %
---                                                           %
>         RESTORE\_SP(fp);                                    %
...                                                           %
{\bf Mutant information:}                                     %
Failure repaired by 148 mutants.                              %
...                                                           %
\#3: delete statement mutant of jsinterp.c:944:               %
                                                              %
            vp[1] = OBJECT\_TO\_JSVAL(thisp);                 %
        \} else \{                                            %
/*MUTANT    ok = OBJ\_GET\_PROPERTY(cx, thisp, id, \&v);*/    %
        \}                                                    %
                                                              %
\end{code}                                                    %
}                                                             %
\caption{Patch and explanation for fault 115}                 %
%\vspace{-0.18in}                                             %
\label{fig:explain}                                           %
\end{figure}                                                  %
\end{comment}                                                 %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \begin{comment}                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                        %
% \subsubsection{Error Explanation}                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                      %
%                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                        %
%                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                        %
 Figure \ref{fig:explain} shows part of the patch for SpiderMonkey fault 115, and the {\bf Repair} output that successfully localizes the fault (the 3rd mutant output), to give some idea of the information our method presents.                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

@@

\subsection{Mutation Analysis Costs}

@@

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}                                                %
{\scriptsize                                                  %
\begin{code}                                                  %
{\bf Diff of old ($<$) vs new ($>$) for 115 patch (portion):} %
...                                                           %
<             vp[1] = OBJECT\_TO\_JSVAL(thisp);               %
<         \} else \{                                          %
<             ok = OBJ\_GET\_PROPERTY(cx, thisp, id, \&v);    %
<         \}                                                  %
...                                                           %
<                   a->avail = (jsuword)sp;                   %
<               \}                                            %
...                                                           %
---                                                           %
>         RESTORE\_SP(fp);                                    %
...                                                           %
{\bf Mutant information:}                                     %
Failure repaired by 148 mutants.                              %
...                                                           %
\#3: delete statement mutant of jsinterp.c:944:               %
                                                              %
            vp[1] = OBJECT\_TO\_JSVAL(thisp);                 %
        \} else \{                                            %
/*MUTANT    ok = OBJ\_GET\_PROPERTY(cx, thisp, id, \&v);*/    %
        \}                                                    %

{\bf Coverage change information:}
...
\#6: 5 mutants (3.38\% of repairs) added jsinterp.c:992:
                   a->avail = (jsuword)sp; /* ADDED */                                                            %
\end{code}                                                    %
}                                                             %
\caption{Patch and explanation for fault 115}                 %
%\vspace{-0.18in}                                             %
\label{fig:explain}                                           %
\end{figure}                                                  %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \begin{comment}                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                        %
% \subsubsection{Error Explanation}                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                      %
%                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                        %
%                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                        %
                                                                                                                                                                                                                                                                             %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\subsection{Coverage Localization}

While {\bf Repair} is often a high-quality localization technique, it often fails to localize a fault at all.  This failure suggested that for the compiler setting, we should consider other localizations methods, even ones we do not consider likely to be helpful in more general settings.  Compiler faults are often so complex and hard to debug that even a somewhat informative localization might be useful.

By definition, when a mutant repairs a test case, it changes the
behavior of the test.  In some cases, this behavioral change may be
limited to changes in program state and data values.  However, the
vast majority of mutant repairs \emph{for a compiler} can be expected to also modify the code coverage of a
test; in our compiler experiments, there were no repairs that did not change
coverage; this would be very unlikely to hold in other software settings, where many bugs related to data values; for well-fuzzed compilers, however, few bugs are simple, e.g., off-by-one bugs in an integer value.  If a fault can be avoided by disabling a
problematic optimization in a compiler, this naturally leads to
changed coverage.  If the fault is due to a bad conditional, where a
program path should include additional code, the repair will often
change the execution to include the omitted code.  As a localization
for a fault, then, we can examine the source statements whose
coverage changed most often in repairs.  Early experiments with this
 approach showed that a useful coverage change localization must  account for the frequency of a
change.  Some coverage changes are extremely common across all
failures, faults, and repairing mutants,
and therefore likely not related to any specific fault.

\begin{quote}
The {\bf Coverage} localization for a failing test case $f \in F$ ($F$
is the set of all failing test cases) ranks
statements by the function $r$ (for rank) where:
%$$U = s : \forall m . \forall t \in F . c(m,t,s) = 1$$
$$C(s) = \sum_{t \in F} (\sum_{m \in R(t)} c(m,t,s))$$
%\[
$$r(s,f) = \sum_{m \in R(f)}\frac{1}{C(s)}c(m,f,s)$$
%\begin{cases}
% \sum_{m \in R(f)}\frac{1}{C(s)}c(m,f,s) & s \not\in U\\
%   0 & s \in U
%\end{cases}
%\]
$c(m,t,s)$ is 1 if coverage of $s$ changes for test $t$
with mutant $m$, and 0 otherwise.  $R(f)$ is the set of mutants repairing $f$.
\end{quote}

That is, the ranking is based on the number of times a statement's
coverage changes its value (covered or not covered) from the original
execution of $f$ in executions of mutants that repair $f$.  Changes are weighted by their inverse frequency over all
failures and all mutants.
Higher values for $r$ result in a higher ranking (more likely to
be faulty).

The coverage localization also provides a kind of explanation, though
a less direct one than with a repair.  For any
interesting line of code in the coverage-change-based localization,
the user can investigate a particular instance of the change,
by selecting a single mutant and stepping through the execution of the
failing test case in a debugger to the point of change.  The user can also
browse through all mutants that produce this coverage change for the test
case.

\begin{figure}                                                %
{\scriptsize                                                  %
\begin{code}                                                  %
{\bf Diff of old ($<$) vs new ($>$) for 115 patch (portion):} %
...                                                           %
<             vp[1] = OBJECT\_TO\_JSVAL(thisp);               %
<         \} else \{                                          %
<             ok = OBJ\_GET\_PROPERTY(cx, thisp, id, \&v);    %
<         \}                                                  %
...                                                           %
<                   a->avail = (jsuword)sp;                   %
<               \}                                            %
...                                                           %
---                                                           %
>         RESTORE\_SP(fp);                                    %
...                                                           %
{\bf Mutant information:}                                     %
Failure repaired by 148 mutants.                              %
...                                                           %
\#3: delete statement mutant of jsinterp.c:944:               %
                                                              %
            vp[1] = OBJECT\_TO\_JSVAL(thisp);                 %
        \} else \{                                            %
/*MUTANT    ok = OBJ\_GET\_PROPERTY(cx, thisp, id, \&v);*/    %
        \}                                                    %

{\bf Coverage change information:}
...
\#6: 5 mutants (3.38\% of repairs) added jsinterp.c:992:
                   a->avail = (jsuword)sp; /* ADDED */                                                            %
\end{code}                                                    %
}                                                             %
\caption{Patch and explanation for fault 115}                 %
%\vspace{-0.18in}                                             %
\label{fig:explain}                                           %
\end{figure}                                                  %

Figure \ref{fig:explain} shows part of the patch for SpiderMonkey fault 115, and the {\bf Repair} and {\bf Coverage} outputs that successfully localize the fault (the 3rd mutant output, and the 6th coverage change output), to give some idea of the information our methods present.  For {\bf Coverage}, it is surprising that the sixth highest ranked change only appeared in 5 of 148 repairs. This change ranked high out of thousands of changes because it was unusual, appearing for only 10 repairs in the entire SpiderMonkey analysis.

@@

\section{Mutation Analysis Costs}

@@

\subsection{Hot and Cold Running Mutants}
